RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-27 paper/paper7/paper7.tex
section 4

\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \emph{sets of constraints}:
\begin{itemize}
	\item $\mathcal{SL}_{0}$: set of constraints with \textbf{severity level \emph{informational}}
	\item $\mathcal{SL}_{1}$: set of constraints with \textbf{severity level \emph{warning}}
	\item $\mathcal{SL}_{2}$: set of constraints with \textbf{severity level \emph{error}}
\end{itemize}
Violations of $\mathcal{SL}_{0}$ constraints point to desirable data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically and/or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that data, not conforming to $\mathcal{SL}_{1}$ but conforming to $\mathcal{SL}_{2}$ constraints, could be processed further,
whereas data, not corresponding to $\mathcal{SL}_{2}$ constraints, cannot be processed further after validation. 
Although, we provide default severity levels for each constraint, validation environments should enable users to adapt constraints' severity levels according to their individual needs.

As $\mathcal{CT}_{B}$ constraints are derived from explicitly stated semantics of vocabularies' data models, 
default severity levels of $\mathcal{CT}_{B}$ constraints are in most cases very strong ($\mathcal{SL}_{2}$) and 
in average stronger than severity levels of $\mathcal{CT}_{S}$ and $\mathcal{CT}_{C}$ constraints.
As a consequence, violating many $\mathcal{CT}_{B}$ constraints is an indicator for bad data quality\footnote{For simplicity reasons, we only assign severity levels to $\mathcal{CT}_{B}$ constraints when they differ from $\mathcal{SL}_{2}$.}.

Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
For some use cases, 
validating constraints of $\mathcal{CT}_{B}$ constraint types may be more important than validating constraints of $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraint types.
For other use cases,
validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
We evaluate a huge amount of metadata and data represented by multiple vocabularies to get an understanding 
(1) which sets of constraint types and 
(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints (see section \ref{evaluation}).

>>>>

\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \emph{sets of constraints}:
\begin{itemize}
	\item $\mathcal{SL}_{0}$: set of constraints with \textbf{severity level \emph{informational}}
	\item $\mathcal{SL}_{1}$: set of constraints with \textbf{severity level \emph{warning}}
	\item $\mathcal{SL}_{2}$: set of constraints with \textbf{severity level \emph{error}}
\end{itemize}
Violations of $\mathcal{SL}_{0}$ constraints point to desirable data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically and/or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that data, not conforming to $\mathcal{SL}_{1}$ but conforming to $\mathcal{SL}_{2}$ constraints, could be processed further,
whereas data, not corresponding to $\mathcal{SL}_{2}$ constraints, cannot be processed further after validation. 
As constraints of $\mathcal{CT}_{B}$ constraint types are derived from explicitly stated semantics of vocabularies, 
their default severity levels are in most cases very strong ($\mathcal{SL}_{2}$) and 
in average stronger than the severity levels of constraints assigned to $\mathcal{CT}_{S}$ and $\mathcal{CT}_{C}$ constraint types.
As a consequence, violating many constraints of $\mathcal{CT}_{B}$ constraint types is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to $\mathcal{CT}_{B}$ constraints in this paper in case they differ from $\mathcal{SL}_{2}$.}.

Although, we provide default severity levels for each constraint, validation environments should enable users to adapt constraints' severity levels according to their individual needs.
Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
For some use cases, 
validating constraints of $\mathcal{CT}_{B}$ constraint types may be more important than validating constraints of $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraint types.
For other use cases,
validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
We evaluate a huge amount of metadata and data represented by multiple vocabularies to get an understanding 
(1) which sets of constraint types and 
(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints (see section \ref{evaluation}).
